---
title: "Applicaton"
date: "`r Sys.Date()`"
#format: 
#  html:
#    page-layout: article
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
params:
  name: "0"
format: html
engine: knitr
filters:
  - webr
---

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/app_par.qmd')
quarto::quarto_preview(pre_fil)
params <- list(name="1")
#lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
```

```{r, echo=F}
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
library(ManifoldDestiny)
library(dplyr)
library(ggplot2)
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(combinat)
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md$tabsets
mda <- md['1']
app1_rp <- selreport(app1,md$app1)
app_a_out <- seloutput(app1_rp)
```





```{r, echo=F}
mda <- md['1']
app1_rp <- selreport(app1,md$app1)
app_a_out <- seloutput(app1_rp)
```

## Application: `r mda$nmn`

### Information
- Election system:
  - Type of race: `r mda$race$rcn` 
  - Candidates: `r mda$race$cnd` 
  - Modes of voting: `r mda$race$mod` 

- $H_0:$ Normal election 
- $H_1:$ Rigged election: 
  - Manifold object `r mda$mtd$sgs$eq[1]`
  - Solved for `r mda$mtd$sgs$va`

[Link to raw data and independent calculcations](`r mda$sht$url`)

---

::: {.panel-tabset}

### `r md$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_a_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### `r md$tabsets[[2]]`
```{r, echo=F, out.width="60%"}
app_a_out[['corxy']]
```
### `r md$tabsets[[3]]`
```{r, echo=F, out.width="60%"}
app_a_out[['qunt']]
```
### `r md$tabsets[[4]]`
```{r, echo=F}
app_a_out[['ro3d']]
```
### `r md$tabsets[[5]]`
```{r, echo=F, out.width="60%"}
app_a_out[['regr']]
```
### `r md$tabsets[[6]]`
```{r, echo=F, out.width="60%"}
app_a_out[['resp']]
```
::: 

---

### Ballot predictions based on limit information implied by the estimated Manifold object(s)

```{r, echo=F}
#app_a_out$cmp[,1] <- c("Mean total votes", "Number of precincts", "Zero prediction error", "In percentage", "Mean", "Standard Deviation", "Max ballot error", "1+/- prediction error", "2+/- prediction error", "2+/- prediction error", "Percentage within +/-3")
#kableExtra::kbl(app_a_out$cmp,row.names=F,col.names=c("Statistic","Value"),digits=2) %>% kableExtra::kable_paper(full_width = F) 
```



