---
title: ""
params:
  name: "0"
---

```{r, echo=F,message=FALSE,warning=FALSE}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
apps <- ManifoldDestiny::app0
adat <- apps[[1]]
amet <- apps[[2]]
cogr <- Countinggraphs(apps[[1]])
selo <- seloutput(selreport(apps))
copl <- cogr$polyc[[1]][[1]]
```




## Application: `r amet$nmn`

### {{< var tabh.h1 >}}

---

::: {.panel-tabset}

### {{< var tabs.h1 >}}

```{r, echo=F}
kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
selo[['corxy']]
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
selo[['qunt']]
```
### {{< var tabs.h4 >}}
```{r, echo=F}
selo[['ro3d']]
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
selo[['regr']]
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
selo[['resp']]
```
::: 


```{r, echo=F}
knitr::knit_exit()
```

### Ballot predictions based on limit information implied by the estimated Manifold object(s)

















## Application: `r #mda$nmn`
### Information
- Election system:
  - Type of race: `r #mda$rcn` 
  - Candidates: `r #mda$cnd` 
  - Modes of voting: `r #mda$mod` 
- $H_0:$ Normal election 
- $H_1:$ Rigged election: 
  - Manifold object $`r #mda$eq[1]`$
  - Solved for `r #mda$va`

[Link to raw data and independent calculcations](`r #mda$url`)


```{r, echo=F}
knitr::knit_exit()
```

---

### Ballot predictions based on limit information implied by the estimated Manifold object(s)

```{r, echo=F}
asop$cmp[,1] <- c("Mean total votes", "Number of precincts", "Zero prediction error", "In percentage", "Mean", "Standard Deviation", "Max ballot error", "1+/- prediction error", "2+/- prediction error", "2+/- prediction error", "Percentage within +/-3")
kableExtra::kbl(asop$cmp,row.names=F,col.names=c("Statistic","Value"),digits=2) %>% kableExtra::kable_paper(full_width = F) 
```










