---
,itle: ""
output: github_document
always_allow_html: true
---

```{r, eval=F, echo=F}
rmarkdown::render("index.Rmd")
```

```{r, echo=F, message=F, warning=F}
### Loading equations
#source('inst/script/stylized.R')
#load("~/research/ManifoldDestiny/data/eqpar.rda")
#modlat <- eqpar$meql
```


```{r, eval=F, echo=F}
pkgdown::build_site()
pkgdown::build_home()
pkgdown::build_articles()
pkgdown::build_news()
usethis::use_news_md("")
git2r::config(user.name = "lotariohw26", user.email = "lotariohw26e@protonmail.com")
system("cp inst/Presentation.html docs/articles/Presentation.html")
system("cp -r inst/libs docs/articles")
#system("cp inst/man_bib.bib docs/stuff/man_bib.bib")
devtools::document(); ManifoldDestiny::bm()
rm(list = c("Countingprocess", "pareq", "Voterdatabase"))
```
Ed. Solomon

> "At the very core of this article lay the assumption of Causality, that the Effect cannot precede the Cause; likewise, the Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate. In a fair election, the aggregate cannot be known until after all ballots are cast; in an election that is unfair, where the aggregate was predetermined, the aggregate becomes the cause and the Mail-in Vote (and/or the Election Day Vote) becomes the effect...and the laws of mathematics allow us to readily discern between which was the cause...and which was the effect."

> To Paraphrase Immanuel Kant:  “The causation is the thing without which, is a condition of possibility of a thing, and so it is satisfied in the thing.”  

<br>
<br>
<br>
<br>
<br>

```{r, echo=F, eval=T}
knitr::knit_exit()
```

# Now
inst/Presentation.Rmd
inst/script/application_dallas.R
inst/script/application_maricopa.R
inst/script/symbolic/pysympy.py

vignettes/Application_Dallas.Rmd
vignettes/Parametric_taut.Rmd



####################################################################3
#' @export Countingprocess
#' @export class Countingprocess
Countingprocess <- setRefClass("Countingprocess", fields=list(sdfc='data.frame',rdfc='data.frame',quintile='data.frame',pardf='data.frame', polyc='list',parameters='list', pareqs='list',plot3dlist='list'))
Countingprocess$methods(initialize=function(sdfinp=NULL,polyn=6,sortby=alpha){

  # Assigning model equations
  rotp <- rprojroot::find_rstudio_root_file()
  mpath <- paste0(rotp,'/data/eqpar.rda')
  load("~/research/ManifoldDestiny/data/eqpar.rda")
  pareqs <<- eqpar

  parameters <<- list(standard=c("x","y","alpha","zeta","lambda"),
  		      hybrid=c("g","h","Omega","lambda","xi"),
		      opposition=c("m","n","Omega","xi","lambda"))

  sdfc <<- sdfinp %>% dplyr::select(pre,a,b,c,d) %>% dplyr::group_by(pre) %>%
    dplyr::arrange(pre) %>% dplyr::mutate(a=sum(a),b=sum(b),c=sum(c),d=sum(d)) %>%
    dplyr::ungroup() %>% dplyr::distinct() %>%
    dplyr::group_by(pre) %>% dplyr::arrange(pre) %>% dplyr::mutate(a=sum(a),b=sum(b),c=sum(c),d=sum(d)) %>%
    dplyr::ungroup() %>% dplyr::distinct() %>%
    dplyr::filter(a>0) %>%
    dplyr::filter(b>0) %>%
    dplyr::filter(c>0) %>%
    dplyr::filter(d>0) %>%
    dplyr::mutate(x=a/(a+b),y=c/(c+d)) %>%
    dplyr::mutate(g=a/(a+d),h=c/(b+c)) %>%
    dplyr::mutate(m=a/(a+c),n=b/(b+d)) %>%
    dplyr::mutate(zeta=(c+d)/(a+b)) %>%
    dplyr::mutate(Omega=(a+b)/(a+b+c+d)) %>%
    dplyr::mutate(Gamma=(b+c)/(a+d)) %>%
    dplyr::mutate(xi=(b+d)/(a+c)) %>%
    dplyr::mutate(alpha=(a+c)/(a+b+c+d),
		 alphac1=Omega*x+(1-Omega)*y,
		 alphac2=(x+zeta*y)/(1+zeta),
		 alphac3=1/(1+xi)) %>%
    dplyr::mutate(lambda=(a+d)/(a+b+c+d),
		 lambdac1=(x+zeta*(1-y))/(zeta+1),
		 lambdac2=(1)/(Gamma+1),
		 lambdac3=(m+xi*(1-n))/(xi+1)) %>%
    dplyr::mutate(Omega=(a+b)/(a+b+c+d),
		 Omegac1=(1)/(1+zeta),
		 Omegac2=(g+Gamma*(1-h))/(Gamma+1),
		 Omegac3=(m+xi*n)/(xi+1)) %>%
    dplyr::mutate(zeta1=(x-alpha)/(alpha-y)) %>%
    dplyr::mutate(xi1=(m-Omega)/(Omega-n)) %>%
    dplyr::mutate(xi2=(m-lambda)/(lambda-(1-n))) %>%
    dplyr::mutate(pri=row_number()/length(pre))

  rdfc <<- sdfc

  # Init values standard form
  polyc[[1]] <<- unname(coef(lm(sdfc$alpha ~ poly(sdfc$pri, polyn, raw=TRUE))))
  # Init values hybrid form
  #polyc[[2]] <<- unname(coef(lm(sdfc$alpha ~ poly(sdfc$pri, polyn, raw=TRUE))))
  ### Init values opposition form
  #polyc[[3]] <<- unname(coef(lm(sdfc$alpha ~ poly(sdfc$pri, polyn, raw=TRUE))))
  ### Init poly

})
Countingprocess$methods(sortpre=function(poly=6,sortby='alpha',selvar=c('x','y','alpha','lambda','zeta')){

 srdfc <- rdfc %>%
    dplyr::select(pre,zeta,all_of(selvar)) %>%
    dplyr::arrange(sortby) %>%
    dplyr::mutate(pri=row_number()/length(pre)) %>%
    dplyr::mutate(zeta_m=mean(zeta)) %>%
    dplyr::mutate(zeta_r=zeta-zeta_m)
    selvar %>% purrr::map(function(x,df=srdfc,p=poly){
	pred <- c(predict(lm(df[[x]] ~ poly(df$pri,p, raw=T))))
	res <- pred - df[[x]]
	data.frame(pred,res) %>% `colnames<-` (c(paste0(x,'_pred'),paste0(x,'_res')))
    }) %>% as.data.frame(.) -> predictor
  quintile <<- dplyr::bind_cols(srdfc, predictor)
})
Countingprocess$methods(riggsta=function(
					 form=1,
					 param=list(pre=c('x','alpha','zeta'), end=c('y','lambda')),
					 polyadj=polyc[[1]]
					 ){

  polycl <- polynom::polynomial(polyadj)
  pardf <<- dplyr::select(quintile,param$pre,param$end) %>%
    # Presetting three parameters
    dplyr::mutate(x_s=x) %>%
    dplyr::mutate(alpha_s=predict(polycl,quintile$x)) %>%
    dplyr::mutate(y_s=0.10) %>%
    # Backsolving for two parameters
    dplyr::mutate(zeta_s=pareq(ste=pareqs$meqs[['zeta_s']][1],lv=list(x=x_s,alpha=alpha_s,y=y_s))) %>%
    dplyr::mutate(lambda_s=pareq(ste=pareqs$meqs[['lambda_s']][1],lv=list(x=x_s,zeta=zeta_s,y=y_s)))

    rdfc[c(param$pre,param$end)] <<- pardf[6:10]
})
Countingprocess$methods(rigghyp=function(sdfinp=NULL){
  # Init values standard form
  k <- function(alpha,x,k,h) eval(parse(text=formula,c(list(alpha=alpha,x=x),list(k=k,h=h))))
  rdfc <<- sdfc %>% dplyr::select(pri,pre,alpha,x,y)
})
Countingprocess$methods(riggopo=function(sdfinp=NULL){
  # Init values standard form
  n <- function(alpha,x,k,h) eval(parse(text=formula,c(list(alpha=alpha,x=x),list(k=k,h=h))))
  rdfc <<- sdfc %>% dplyr::select(pri,pre,alpha,x,y)
})
#' @export Countinggraphs
#' @exportClass Countinggraphs
Countinggraphs <- setRefClass("Countinggraphs", contains = c('Countingprocess'))
Countinggraphs$methods(plot2d=function(selvp=c("x","y","alpha"),selvl=c("x_pred","y_pred","alpha_pred")){

    longdf <- tidyr::pivot_longer(quintile,all_of(c(selvp,selvl)))
    ggplot2::ggplot(data=longdf) +
	geom_line(data=filter(longdf,name%in%selvl),aes(x=pri,y=value, color=name)) +
	geom_point(data=filter(longdf,name%in%selvp),aes(x=pri,y=value, color=name)) +
	#labs(x=selv[1],y=selv[2],title="") +
	ggplot2::theme_bw()
})
#Countinggraphs$methods(plotxy=function(selv=c("x","y")){
#
#    widedf <- sdfc
#    ggplot2::ggplot(data=widedf,aes_string(x=selv[1],y=selv[2])) +
#	geom_point() +
#	geom_smooth(method=lm,se=F) +
#        #ggpubr::stat_regline_equation(label.x=0,label.y=0.10) +
#        ggpubr::stat_cor() +
#   	labs(x=selv[1],y=selv[2],title="") +
#    	ggplot2::theme_bw()
#})
#Countinggraphs$methods(resplot=function(resvar=c("zeta_r","alpha_res")){
#
#  x <- quintile[paste0(resvar[1])]
#  y <- quintile[paste0(resvar[2])]
#  quintile$z <<- x*y
#  ggplot2::ggplot(data=quintile,aes_string(resvar[1],resvar[2])) +
#    geom_smooth(method="lm") +
#    geom_point() +
#    #stat_regline_equation(label.x=0,label.y=0.10) +
#    #stat_cor(label.x=0,label.y=0.15) +
#    ggplot2::theme_bw()
#})
#Countinggraphs$methods(plotly3d=function(
#					 partition=1,
#					 sel=list(1:5,6:10),
#					 selid=1
#					 ){
#
#  rdfcpar <- rdfc %>% dplyr::select(parameters[[partition]])
#  mrdfc <- as.matrix(rdfcpar)
#  combi <- combinat::combn(5, 3)
#  seq(1,dim(combi)[2]) %>% purrr::map(function(x,comb=combi,df=rdfcpar){
#  gdf <- df %>% dplyr::select(combi[,x])
#  mrdfc <- as.matrix(gdf)
#  x <- mrdfc[,1]
#  y <- mrdfc[,2]
#  z <- mrdfc[,3]
#  plotly::plot_ly(x=x,y=y,z=z,type="scatter3d", mode="markers") %>%
#  plotly::layout(scene = list(xaxis = list(title = names(gdf)[1]),
#  yaxis = list(title = names(gdf)[2]),
#  zaxis = list(title = names(gdf)[3]))) }) ->> plot3dlist
#
#  ohtml <- div(class="row", style = "display: flex; flex-wrap: wrap; justify-content: center",
#  	 div(plot3dlist[sel[[1]]], class="column"),
#  	 div(plot3dlist[sel[[2]]],class="column"))
#  list(page=htmltools::browsable(ohtml),ohtml=ohtml,one=plot3dlist[[selid]])
#})
#' @export Countingtables
#' @exportClass Countingtables
Countingtables <- setRefClass("Countingtables", contains = c('Countingprocess'), fields = list(ghi='list'))
###########################################################################################################################################################
#rootsolving <- function(k=NULL,c=NULL){
#  #reticulate::repl_python('../inst/script/rootsolving/fqs.py')
#  #os <-reticulate::import("fqs")
#  A <- 1
#  B <- 1
#  C <- 1
#  D <- 1
#  E <- 1
#  p <- c(A,B,C,D,E)[1:4]
#  #os$quartic_roots(p)
#}
##rootsolving()
############################################################################################################################################################
