---
,itle: ""
output: github_document
always_allow_html: true
---

```{r, eval=F, echo=F}
rmarkdown::render("index.Rmd")
```

```{r, echo=F, message=F, warning=F}
### Loading equations
#source('inst/script/stylized.R')
#load("~/research/ManifoldDestiny/data/eqpar.rda")
#modlat <- eqpar$meql
```


```{r, eval=F, echo=F}
pkgdown::build_site()
pkgdown::build_home()
pkgdown::build_articles()
pkgdown::build_news()
usethis::use_news_md("")
system("cp inst/Presentation.html docs/articles/Presentation.html")
system("cp -r inst/libs docs/articles")
#system("cp inst/man_bib.bib docs/stuff/man_bib.bib")
```

Ed. Solomon

> "At the very core of this article lay the assumption of Causality, that the Effect cannot precede the Cause; likewise, the Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate. In a fair election, the aggregate cannot be known until after all ballots are cast; in an election that is unfair, where the aggregate was predetermined, the aggregate becomes the cause and the Mail-in Vote (and/or the Election Day Vote) becomes the effect...and the laws of mathematics allow us to readily discern between which was the cause...and which was the effect."

> To Paraphrase Immanuel Kant:  “The causation is the thing without which, is a condition of possibility of a thing, and so it is satisfied in the thing.”  

<br>
<br>
<br>
<br>
<br>

```{r, echo=F, eval=T}
knitr::knit_exit()
```

# Now
inst/Presentation.Rmd
inst/script/application_dallas.R
inst/script/application_maricopa.R
