---
title: ""
output: html_document
---

```{r eval=F, echo=F}
setwd(rprojroot::find_rstudio_root_file())
filp <- 'vignettes/abc.Rmd'
rmarkdown::render(filp)
system('brave vignettes/abc.html')
```

```{r setup, echo=F}
library(ManifoldDestiny)
load(paste0(abs_path(),'/data/eqpar.rda'))
load(paste0(abs_path(),'/data/stickers.rda'))
modlat <- eqpar$meql
labs <- stickers[['parameters']]
library(dplyr)
library(huxtable)
lego_hux <- as_hux(matrix(1:16, 4, 4)) %>% 
      set_background_color(1:2, 1:2, "red") %>% 
      set_background_color(1:2, 3:4, "yellow") %>% 
      set_background_color(3:4, 1:2, "darkgreen") %>% 
      set_background_color(3:4, 3:4, "blue") %>% 
      set_text_color(3:4, 1:4, "white") %>% 
      set_all_borders(brdr(2, "solid", "white"))
lego_hux %>% set_caption("Original table")
```


### Standard form
# Step 1
# Step 2
# Step 3
Parameters: $x$, $y$, $\zeta$, $\alpha$, $\lambda$

\begin{equation*}
x=`r modlat$x_s[1]`
\end{equation*}
\begin{equation*}
y=`r modlat$y_s[1]`
\end{equation*}
\begin{equation*}
\zeta=`r modlat$zeta_s[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lambda_s[1]`=`r modlat$lambda_s[2]`
\end{equation*}

# Step 4
### Hybrid form
Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$

\begin{equation*}
g=`r modlat$g_h[1]`
\end{equation*}
\begin{equation*}
h=`r modlat$h_h[1]`
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1]`=`r modlat$Omega_h[2]`
\end{equation*}

# Step 5

# Step 6
# Step 7
# Step 8


