---
title: " "
output: html_document
---

```{r, eval=F, echo=F}
filn <- 'Parametric_taut'
abs_path <- function(){rprojroot::find_rstudio_root_file()}
rmarkdown::render(paste0(abs_path(),'/vignettes/',filn,'.Rmd'))
#abs_path <- function(){rprojroot::find_rstudio_root_file()}
#fdm <- paste0(abs_path(),'/inst/script/symbolic/pysympy.py')
#reticulate::source_python(fdm)
#eqpar <- list(meql=reticulate::py$modeql,meqs=reticulate::py$modeqs)
## Saving data
#usethis::use_data(eqpar, overwrite = TRUE)
```

```{r include=FALSE}
library(ManifoldDestiny)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(randNames)
library(openxlsx)
library(patchwork)
library(writexl)
library(plotly)
library(ViewPipeSteps)
library(RefManageR)
library(ggpubr)
```

```{r, eval=T, echo=F, message=F, warning=F}
### Loading equations
abs_path <- function(){rprojroot::find_rstudio_root_file()}
load(paste0(abs_path(),'/data/eqpar.rda'))
modlat <- eqpar$meql
```

### Standard form
Parameters: $x$, $y$, $\alpha$, $\lambda$ $\zeta$

\begin{equation*}
x=`r modlat$x_s[1]`
\end{equation*}
\begin{equation*}
y=`r modlat$y_s[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`=`r modlat$alpha_s[3]`=`r modlat$alpha_s[4]`
\end{equation*}
\begin{equation*}
\zeta=`r modlat$zeta_s[1]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lambda_s[1]`
\end{equation*}

---

### Hybrid form
Parameters: $g$, $h$, $\alpha$, $\Omega$, $\Gamma$

\begin{equation*}
g=`r modlat$g_h[1]`
\end{equation*}
\begin{equation*}
h=`r modlat$h_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1]`
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}

---

### Opposition form
Parameters: $m$, $n$, $\Omega$, $\lambda$, $\xi$

\begin{equation*}
m=`r modlat$g_h[1]`
\end{equation*}
\begin{equation*}
n=`r modlat$h_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$Omega_h[1]`
\end{equation*}
\begin{equation*}
\xi=`r modlat$Gamma_h[1]`
\end{equation*}


## Numerical testing of equations

```{r, eval=T, message=F, warning=F, echo=F}
sourcef <- 'stylized.R'
abs_path <- function(){rprojroot::find_rstudio_root_file()}
source(paste0(abs_path(),'/inst/script/',sourcef))
```

```{r}
gcou <- Countinggraphs(votr)
```






