---
title: "Stylized_model"
output: html_document
---

```{r include=FALSE}
library(ManifoldDestiny)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(randNames)
library(openxlsx)
library(patchwork)
library(writexl)
library(plotly)
library(ViewPipeSteps)
library(RefManageR)
library(ggpubr)
```

```{r, eval=T, echo=F, message=F, warning=F}
### Loading equations
#source('inst/script/stylized.R')
load("~/research/ManifoldDestiny/data/eqpar.rda")
modlat <- eqpar$meql
```

### Standard form
Parameters: $x$, $y$, $\alpha$, $\lambda$ $\zeta$

\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`=`r modlat$alpha_s[3]`=`r modlat$alpha_s[4]`
\end{equation*}

---

### Hybrid form
Parameters: $g$, $h$, $\alpha$, $\Omega$, $\Gamma$

\begin{equation*}
\alpha=`r modlat$alpha_s[2]`=`r modlat$alpha_s[3]`=`r modlat$alpha_s[4]`
\end{equation*}

---

### Opposition form
Parameters: $m$, $n$, $\Omega$, $\lambda$, $\xi$

\begin{equation*}
\alpha=`r modlat$alpha_s[2]`=`r modlat$alpha_s[3]`=`r modlat$alpha_s[4]`
\end{equation*}

