---
title: " "
output: html_document
---

```{r, eval=F, echo=F}
library(ManifoldDestiny)
rmarkdown::render(paste0(abs_path(),'/vignettes/Parametric_taut.Rmd'))
system(paste0('brave ',paste0(abs_path(),'/vignettes/Parametric_taut.html')))
sympupd()
```
```{r include=FALSE}
library(ManifoldDestiny)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(randNames)
library(openxlsx)
library(patchwork)
library(writexl)
library(plotly)
library(ViewPipeSteps)
library(RefManageR)
library(ggpubr)
```


```{r, eval=T, echo=F, message=F, warning=F}
### Loading equations
load(paste0(abs_path(),'/data/eqpar.rda'))
modlat <- eqpar$meql
```

### Standard form
Parameters: $x$, $y$, $\zeta$, $\alpha$ $\lambda$

\begin{equation*}
x=`r modlat$x_s[1]`
\end{equation*}
\begin{equation*}
y=`r modlat$y_s[1]`
\end{equation*}
\begin{equation*}
\zeta=`r modlat$zeta_s[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lambda_s[1]`=`r modlat$lambda_s[2]`
\end{equation*}

---

### Hybrid form
Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$

\begin{equation*}
g=`r modlat$g_h[1]`
\end{equation*}
\begin{equation*}
h=`r modlat$h_h[1]`
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1]`=`r modlat$Omega_h[2]`
\end{equation*}

### Opposition form
Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$

\begin{equation*}
n=`r modlat$n_o[1]`
\end{equation*}
\begin{equation*}
m=`r modlat$m_o[1]`
\end{equation*}
\begin{equation*}
\xi=`r modlat$xi_o[1]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lambda_o[1]`=`r modlat$lambda_o[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
\end{equation*}


