---
title: ""
output: html_document
---

```{r, eval=F, echo=F}
filn <- 'Parametric_taut'
abs_path <- function(){rprojroot::find_rstudio_root_file()}
ful_path <- paste0(abs_path(),'/vignettes/',filn)
rmarkdown::render(paste0(ful_path,'.Rmd'))
system(paste0('brave ',ful_path,'.html'))
sympupd()
```

```{r include=FALSE}
library(ManifoldDestiny)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(randNames)
library(openxlsx)
library(patchwork)
library(writexl)
library(plotly)
library(ViewPipeSteps)
library(RefManageR)
library(ggpubr)
```

```{r, eval=T, echo=F, message=F, warning=F}
### Loading equations
abs_path <- function(){rprojroot::find_rstudio_root_file()}
load(paste0(abs_path(),'/data/eqpar.rda'))
modlat <- eqpar$meql
```

### Standard form
Parameters: $x$, $y$, $\alpha$, $\lambda$ $\zeta$

\begin{equation*}
x=`r modlat$x_s[1]`
\end{equation*}
\begin{equation*}
y=`r modlat$y_s[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
\end{equation*}
\begin{equation*}
\zeta=`r modlat$zeta_s[1]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lambda_s[1]`
\end{equation*}

---

### Hybrid form
Parameters: $g$, $h$, $\alpha$, $\Omega$, $\Gamma$

\begin{equation*}
g=`r modlat$g_h[1]`
\end{equation*}
\begin{equation*}
h=`r modlat$h_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1]`
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}

---

### Opposition form
Parameters: $m$, $n$, $\Omega$, $\lambda$, $\xi$

\begin{equation*}
m=`r modlat$m_o[1]`
\end{equation*}
\begin{equation*}
n=`r modlat$n_o[1]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_o[1]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lambda_o[1]`
\end{equation*}
\begin{equation*}
\xi=`r modlat$xi_o[1]`
\end{equation*}

## Numerical testing of equations

```{r}
library(dplyr)
abs_path <- function(){rprojroot::find_rstudio_root_file()}
source(paste0(abs_path(),'/R/misc.R'))
source(paste0(abs_path(),'/R/class.R'))
snr <- 1
set.seed(snr)
##################################################################################################
#### I: Voterdatabase ###
## Inititating
agebracketmax <- c(18,100,1000)
regf <- 0.8
numprec <- 200
vrdf <- Voterdatabase(agebracketmax,numprec,regf,namebase='default',newdraw=T)
###### Realization of DGP
probwset <- c(0.50,0.05)
probvset <- list(c(0.70,0.30,0.00),c(0.30,0.70,0.00))
Znr <- c(0,1)
vrdf$realizedgp(probv=probvset,Ztech=Znr)
votr <- vrdf$voterrollrealized
################################################################################################33
#### A) Fair ###
gcou <- Countinggraphs(votr)
gcou$rdfc
```


